%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Paper.Id} % Organization
    {Indonesia} % Location
    {Jan. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working in the Payment Gateway Business Unit within the Integration Team, focusing on building a new Payment Gateway, expanding and maintaining payment integrations.}
        \item {Integrated payment gateway systems with multiple bank partners, implementing account inquiry, fund transfers, transaction status inquiries, balance checks, and bank statement retrieval while ensuring compliance with SNAP Standards.}
        \item {Established and standardized the onboarding process for the Payment Gateway Business Unit, ensuring a smoother transition for new engineers by providing clear documentation, best practices, and integration guidelines.}
        \item {\textbf{Tech Stack:} Golang, MySQL, RabbitMQ, GCP}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Logisly} % Organization
    {Indonesia} % Location
    {Jun. 2023 - Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Internal Application using AppSheet to streamline Transporter Relation, including Task Assignment, Task Tracker, and Task Management.}
        \item {Redesigned the Payment Request Invoice to accommodate additional information while maintaining a clean and organised appearance, improving the invoice's usability and effectiveness.}
        \item {Created an Open API to enable shippers to consume essential order and order details data securely. Implemented an authentication system with API keys/tokens to ensure data security and documented the API using Swagger.}
        \item {\textbf{Tech Stack:} Yii, MySQL, MongoDB, Redis, React, AppSheet}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer Intern} % Job title
    {Suitmedia} % Organization
    {Indonesia} % Location
    {May 2023 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Expanded and enhanced the existing system for a prominent client specialising in outdoor equipment, including Store, Warehouse Management System (WMS), and Order Management System (OMS).}
        \item {Implemented new features for pick-up, booking, and delivery processes, enhancing the overall functionality of the system.}
        \item {\textbf{Tech Stack:} .NET (C\#), Entity Framework, Hangfire, MySQL, RabbitMQ}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer Intern} % Job title
    {Pintarnya} % Organization
    {Indonesia} % Location
    {May 2022 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built features and optimised API endpoints for improved performance in Pintarnya Kerja and Pintarnya Operational Dashboard (POD).}
        \item {Integrated Pintarnya's job listings with various job portals, such as Google Jobs, Indeed, Jooble, and Trovit.}
        \item {Reduced GMaps API costs by approximately Rp 40 million per month by scraping Indonesian geospatial data.}
        \item {\textbf{Tech Stack:} Golang, PostgreSQL, GCP}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}