%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventrycompany
    {Software Engineer} % Job title
    {Paper.Id} % Organization
    {Indonesia} % Location
    {Jan. 2025 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Achieved \textbf{99\% Payout Success Rate} (\textbf{5.4T IDR TPV}) and \textbf{90\% Payment Success Rate} (\textbf{200B IDR TPV}) through partner integrations, asynchronous processing, exponential backoff, and intelligent routing.}
        \item {\textbf{Led partner integrations} and optimized Cross-Border payout systems handling \textbf{64B IDR TPV}, expanding currency and country support with robust retry mechanisms.}
        \item {\textbf{Led end-to-end development} of \textbf{Fraud Detection System (FDS)} and \textbf{Anti-Money Laundering (AML)} integrations with Fraudnet and Advance.ai, strengthening platform security and compliance.}
        \item {Built log explorer and query workflow features for internal AI tools, reducing manual debugging effort for engineering teams.}
        \item {\textbf{Tech Stack:} Golang, MySQL, RabbitMQ, GCP, Redis, Rust}
      \end{cvitems}
    }
    {Paper.id is a leading Indonesian B2B payment and invoicing solution.} % Company description

%---------------------------------------------------------
  \cventrycompany
    {Backend Engineer} % Job title
    {Logisly} % Organization
    {Indonesia} % Location
    {Jun. 2023 - Dec. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Built internal application using AppSheet to streamline Transporter Relations workflow, covering task assignment, tracking, and management.}
        \item {Redesigned Payment Request Invoice system for improved usability while maintaining clean UI/UX.}
        \item {Designed and implemented secure Open API for shippers with token-based authentication and Swagger documentation.}
        \item {\textbf{Tech Stack:} Yii, MySQL, MongoDB, Redis, React, AppSheet}
      \end{cvitems}
    }
    {Indonesia's largest B2B digital trucking platform connecting shippers with verified carriers.}

%---------------------------------------------------------
  \cventrycompany
    {Backend Engineer Intern} % Job title
    {Suitmedia} % Organization
    {Indonesia} % Location
    {May 2023 - Sep. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Enhanced e-commerce platform for major outdoor equipment client, spanning Store, Warehouse Management (WMS), and Order Management (OMS) systems.}
        \item {Implemented end-to-end features for pick-up, booking, and delivery workflows, improving operational efficiency.}
        \item {\textbf{Tech Stack:} .NET (C\#), Entity Framework, Hangfire, MySQL, RabbitMQ}
      \end{cvitems}
    }
    {Leading Indonesian digital agency specializing in web/app development and digital transformation.}

%---------------------------------------------------------
  \cventrycompany
    {Backend Engineer Intern} % Job title
    {Pintarnya} % Organization
    {Indonesia} % Location
    {May 2022 - Aug. 2022} % Date(s)
    {
      \begin{cvitems}
        \item {Built and optimized API endpoints for Pintarnya Kerja and Operational Dashboard, improving application performance.}
        \item {Integrated job listings platform with Google Jobs, Indeed, Jooble, and Trovit, expanding market reach.}
        \item {Reduced GMaps API costs by \textbf{Rp 40M/month} by building Indonesian geospatial data pipeline.}
        \item {\textbf{Tech Stack:} Golang, PostgreSQL, GCP}
      \end{cvitems}
    }
    {Employment platform for Indonesia's blue-collar workers, offering job matching and financial services.}

%---------------------------------------------------------
\end{cventries}
